cchecks
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.com/ropenscilabs/cchecks.svg?branch=master)](https://travis-ci.com/ropenscilabs/cchecks)
[![codecov.io](https://codecov.io/github/ropenscilabs/cchecks/coverage.svg?branch=master)](https://codecov.io/github/ropenscilabs/cchecks?branch=master)

R client for the CRAN checks API at <https://cranchecks.info>

[CRAN checks API docs][docs]

authentication is only needed for the CRAN checks API for the functions that start with `cchn`

## Install

```{r eval=FALSE}
remotes::install_github("ropenscilabs/cchecks")
```

```{r}
library("cchecks")
```

## heartbeat

```{r}
cch_heartbeat()
```

## packages

all

```{r}
cch_pkgs(limit = 1)
```

by name

```{r}
x <- cch_pkgs(c("geojsonio", "leaflet", "MASS"))
lapply(x, "[[", c("data", "summary"))
```

## maintainers

all

```{r}
cch_maintainers(limit = 1)
```

by name

```{r}
cch_maintainers(c("maelle.salmon_at_yahoo.se", "13268259225_at_163.com"))
```

## notifications

- `cchn_register()`: 
  - register your email address
  - validation email sent to user right away with token
  - all `cch_notif_*` fxns use this cached token
- `cchn_rule_list()`: list your own rules
- `cchn_rule_get()`: get a rule by id
- `cchn_rule_add()`: create a rule
- `cchn_rule_delete()`: delete a rule by id (get id from `cchn_rule_list`)

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/cchecks/issues).
* License: MIT
* Get citation information for `cchecks` in R doing `citation(package = 'cchecks')`
* Please note that this project is released with a [Contributor Code of Conduct][coc]. By participating in this project you agree to abide by its terms.

[docs]: https://cranchecks.info/docs
[coc]: https://github.com/ropenscilabs/cchecks/blob/master/CODE_OF_CONDUCT.md
