cchecks
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.com/ropenscilabs/cchecks.svg?branch=master)](https://travis-ci.com/ropenscilabs/cchecks)
[![codecov.io](https://codecov.io/github/ropenscilabs/cchecks/coverage.svg?branch=master)](https://codecov.io/github/ropenscilabs/cchecks?branch=master)

R client for the cran checks API at <https://cranchecks.info>

[Cran checks API docs][docs]

there's no authentication needed

## Install

Development version

```{r eval=FALSE}
devtools::install_github("ropenscilabs/cchecks")
```

```{r}
library("cchecks")
```

## heartbeat

```{r}
cch_heartbeat()
```

## packages

all

```{r}
cch_pkgs(limit = 1)
```

by name

```{r}
x <- cch_pkgs(c("geojsonio", "leaflet", "MASS"))
lapply(x, "[[", c("data", "summary"))
```

## maintainers

all

```{r}
cch_maintainers(limit = 1)
```

by name

```{r}
cch_maintainers(c("123saga_at_gmail.com", "13268259225_at_163.com"))
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/cchecks/issues).
* License: MIT
* Get citation information for `cchecks` in R doing `citation(package = 'cchecks')`
* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

[docs]: https://cranchecks.info/docs
